From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-17 paper.tex
Split the results tables into attentions results and with-me-ness results
+ added a placeholder for the with-me-ness figure

\begin{table}[h!]
	\centering
    \caption{Tracking accuracy in face-to-face scenario\fixme{std dev needed!}}
	\begin{tabular}{|c|c|c|c|c|c|c|c|} \hline
	\small Subject & 1 & 2 & 3 & 4 & 5 & 6 & Avg\\ \hline
	\small Track(\%) & \small88.2 & \small83.5 & \small90.5 & \small83.1 & \small87.9 & \small85.0 & \small86.4 \\ \hline
	\begin{tabular}{@{}c@{}}\small Real vs \\ \small expected(\%)\end{tabular} & \small92.6 & \small88.8  & \small95.8 & \small93.1 & \small96.5 & \small89.6 & \small92.7 \\ \hline
	\begin{tabular}{@{}c@{}}\small Real vs \\ \small captured(\%)\end{tabular} & \small61.1 & \small85.5 & \small80.8 & \small62.2 & \small63.4 & \small83.9 & \small72.8 \\ \hline
	\begin{tabular}{@{}c@{}}\small Cosine \\ \small affinity \end{tabular} & \small0.73 & \small0.82 & \small0.87 & \small0.73 & \small0.77 & \small0.89 & \small0.8 \\ \hline
	\end{tabular}
	\label{tab:results}
\end{table}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.81\columnwidth]{realCaptured}
    \caption{\small Real VFoA of subject 4 accoding to two observer's
    assessment. In green, the obtained VFoA using our approach and in cyan, the
    matching between them. Finally, the correspondent numbers with figure \ref{fig:bitmap}.}

    \label{fig:realCaptured}
\end{figure*}

>>>>

\begin{table}[h!]
	\centering
    \caption{\textbf{Results of attention tracking accuracy}. \emph{Head pose} is the percentage of total time during which the head pose of the participant was successfully estimated;}
	\begin{tabular}{|c|c|c|c|c|c|c|c|c|} \hline
        \small \textbf{Subject} & 1 & 2 & 3 & 4 & 5 & 6 & Avg. & Std dev\\ \hline
        \small Head pose (\%) & \small88.2 & \small83.5 & \small90.5 & \small83.1 & \small87.9 & \small85.0 & \small86.4 & \\ \hline
            \begin{tabular}{@{}c@{}}\small Groundtruth \vs \\ \small robot (\%)\end{tabular} & \small61.1 & \small85.5 & \small80.8 & \small62.2 & \small63.4 & \small83.9 & \small72.8 & \\ \hline
        \begin{tabular}{@{}c@{}}\small Agreement ($\alpha$)\end{tabular} &  & & & & & & & \\ \hline
            \begin{tabular}{@{}c@{}}\small Cosine \\ \small affinity \end{tabular} & \small0.73 & \small0.82 & \small0.87 & \small0.73 & \small0.77 & \small0.89 & \small0.8 & \\ \hline
	\end{tabular}
	\label{tab:results}
\end{table}

@@

\begin{table}[h!]
	\centering
    \caption{\textbf{Results of attention tracking accuracy}. \emph{Head pose} is the percentage of total time during which the head pose of the participant was successfully estimated;}
	\begin{tabular}{|c|c|c|c|c|c|c|c|c|} \hline
        \small \textbf{Subject} & 1 & 2 & 3 & 4 & 5 & 6 & Avg. & Std dev\\ \hline
        \begin{tabular}{@{}c@{}}\small Groundtruth vs \\ \small expected(\%)\end{tabular} & \small92.6 & \small88.8  & \small95.8 & \small93.1 & \small96.5 & \small89.6 & \small92.7 & \\ \hline
        \begin{tabular}{@{}c@{}}\small Groundtruth \\ \small Agreement ($\alpha$)\end{tabular} &  & & & & & & & \\ \hline
            \begin{tabular}{@{}c@{}}\small Robot vs \\ \small expected(\%)\end{tabular} &  & & & & & & & \\ \hline
        \begin{tabular}{@{}c@{}}\small Robot \\ \small Agreement ($\alpha$)\end{tabular} &  & & & & & & & \\ \hline
	\end{tabular}
	\label{tab:results}
\end{table}

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{with-me-ness}
    \caption{\small \textbf{With-me-ness}. Evolution of the level of
    \emph{with-me-ness} over a 20min long child-robot interaction. The diagram
    is identical to Figure~\ref{fig:realExpected} with the \emph{expected}
    attentional targets added in green. The bottom curves represent the levels
    of with-me-ness (since the beginning of the interaction), computed following
    Algorithm~\ref{alg:with-me-ness}. The blue line is with-me-ness as estimated by
    the robot, the orange line is with-me-ness computed from manually annotated
    focuses of attention. The ``holes'' in the with-me-ness computed by the
    robot correspond to period of time where the child's face is not detected.}

    \label{fig:with-me-ness}
\end{figure*}
